Why robot programming is hard

### 2014-08-28 paper.tex
Work in progress

@@

\item {\bf Goal specification}: some tasks are easy to describe, such as navigation goals specified by a single point in 3-dimensional space. Other goals, such as washing the dishes or tidying up, are more difficult to specify. Successful completion may be more dependent on how exactly the robot performs the task. Generally speaking, the more difficult it is to frame the goal specification, the more difficult the programming task will be~\cite{ko-vlhcc04}.
% REF: something from the EUP literature?

@@

For personal robotics to truly succeed, regular people will need to use robot programming interfaces to tell robots what to do. These interfaces for robot programming will need to be simple enough for ordinary consumers to be able to pick up and use. In this article I detail some of the challenges that make robot control such an inherently difficult problem.

The explanation begins with a look at the state of the art in robot software today.

% Until users are able to instruct robots quickly and with low effort, personal robotics will be limited to niche markets.  Why is end user robot programming so challenging? Several compounding factors make it more difficult than normal computer use.

@@

In order to deal with these various types of uncertainty, professional programmers learn to use probabilistic models~\cite{darwiche-cacm10} and craft fault-tolerant code~\cite{wright-cacm09} with frequent error checking, which seems like too much to ask of casual programmers who just to teach their robot to do something useful in the home.

%Most end user programming systems to date simply ignore the problem of uncertainty. For robot programming to be successful, we will need to develop easily-understandable paradigms for handling uncertainty.

>>>>

% Hai Nguyen's ROCON
% Maya's Robot PBD
% Strips style robot planning

@@

\item {\bf Goal specification}: some tasks are easy to describe, such as navigation goals specified by a single point in 3-dimensional space. Other goals, such as washing the dishes or tidying up, are more difficult to specify. Successful completion may be more dependent on how exactly the robot performs the task. Generally speaking, the more difficult it is to frame the goal specification, the more difficult the programming task will be~\cite{ko-vlhcc04}.

@@

For personal robotics to truly succeed, regular people will need to use robot programming interfaces to tell robots what to do. These interfaces for robot programming will need to be simple enough for ordinary consumers to be able to pick up and use. Until users are able to instruct robots quickly and with low effort, personal robotics will be limited to niche markets. Why is end user robot programming so challenging? Several compounding factors make it more difficult than normal computer use.

The story begins with a look at the state of the art in robot software today.

@@

In order to deal with these various types of uncertainty, professional programmers learn to use probabilistic models~\cite{darwiche-cacm10} and craft fault-tolerant code~\cite{wright-cacm09} with frequent error checking. Nguyen's ROS Commander (ROSCo) system is an end-user programming system aimed to enable home users to define new behaviors for PR2 robots by visually crafting finite state machines~\cite{nguyen-icra13}. ROSCo XXX TODO

which seems like too much to ask of casual programmers who just want to teach their robot to do something useful in the home.
